---
title: "DAY 2"
output: html_notebook
---

```{r}
library(tidyverse)
library(janitor)

steam <- read_csv("raw_data/steam_checkpoint.csv")
```

Where was i?

```{r}
games_pre_cleaned <- read_csv("raw_data/Cleaned Data 2 GVGS&R.csv")
```

```{r}
games_pre_cleaned
```
How dare you do the work for me

```{r}
games_raw <- read_csv("raw_data/Raw Data GVGS&R.csv")
```

```{r}
games_raw %>% 
  filter(Name == "Minecraft")
```
Why does everyone have the same dataset

back to steam i guess

```{r}
steam
```

```{r}
steam %>% 
  distinct(genres)
```

Already have F2P covered by another column, so we can drop that in genres

```{r}
steam %>% 
  mutate(genres = str_remove_all(genres, "Free to Play")) %>% 
  filter(free_to_play == TRUE)
```

Is this worth doing?
Duplicated info doesn't hurt i suppose - leave it for now

single player?

```{r}
steam <- steam %>% 
  mutate(singleplayer = case_when(
    str_detect(categories, "Single-player") ~ TRUE,
    str_detect(steamspy_tags, "Singleplayer") ~ TRUE,
    TRUE ~ FALSE
  ),.before = multiplayer)
```

```{r}
steam %>% 
  filter(free_to_play == TRUE) 
```
```{r}
steam
```
```{r}
# adding column to simplify ratings 
steam <- steam %>% 
  mutate(total_reviews = positive_ratings +  negative_ratings) %>% 
  arrange(desc(total_reviews)) %>% 
  mutate(percent_positive_reviews = positive_ratings / total_reviews) %>% 
  mutate(general_rating = case_when(
    total_reviews > 1000 & percent_positive_reviews >= 0.95 ~ "Extremely Positive",
    total_reviews > 1000 & percent_positive_reviews >= 0.75 ~ "Positive",
    total_reviews > 1000 & percent_positive_reviews >= 0.55 ~ "Mostly Positive",
    total_reviews > 1000 & percent_positive_reviews >= 0.50 ~ "Mixed" ,
    total_reviews > 1000 & percent_positive_reviews >= 0.35 ~ " Mostly Negative",
    total_reviews > 1000 & percent_positive_reviews >= 0.15 ~ "Negative",
    total_reviews > 1000 & percent_positive_reviews < 0.15 ~ "Extremely Negative",
    positive_ratings == 0 ~ "No Positive Reviews",
    negative_ratings == 0 ~ "No Negative Reviews",
    positive_ratings & negative_ratings == 0 ~ "No Reviews",
    total_reviews < 1000 ~ "Not Enough Reviews",
    TRUE ~ "No Data"
  ),.before = positive_ratings) %>% 
  select(-percent_positive_reviews)
```



```{r}
backloggd <- read_csv("clean_data/backloggd_clean.csv")
```

```{r}
backloggd
```


```{r}
games_raw <- games_raw %>% 
  clean_names()
```

```{r}
# Platform isn't a genre - correcting
games_raw <- games_raw %>% 
  mutate(genre = case_when(
    genre == "Platform" ~ "Platformer",
    TRUE ~ genre
  ))
```

```{r}
nintendo_published <- games_raw %>% 
  filter(publisher == "Nintendo")
```

```{r}
genre_publisher_sales <- games_raw %>%  
  group_by(publisher, genre) %>% 
  summarise(sum(global_sales)) %>% 
  arrange(desc(`sum(global_sales)`))
```
```{r}
write_csv(genre_publisher_sales, "clean_data/genre_by_publisher.csv")
```

```{r}
genre_publisher_sales %>% 
  filter(publisher == "From Software")
```

```{r}
games_raw %>% 
  distinct(rating)
```


```{r}
# clarifying that the rating is for ESRP - the american system
games_raw <- games_raw %>% 
  rename("esrp" = "rating") 
```

```{r}
# Adding PEGI equivalent 
games_raw <- games_raw %>% 
  mutate(pegi_equivalent = case_when(
    esrp == "EC" ~ "3",
    esrp == "E" ~ "7",
    esrp == "E10+" ~ "12",
    esrp == "T" ~ "16",
    esrp == "M" ~ "18",
    esrp == "AO" ~ "18",
    esrp == "K-A" ~ "7",
    esrp == "RP" ~ "No Rating",
    TRUE ~ "No Rating Found"
  )) 
  
```

```{r}
total_sales_by_genre <- games_raw %>% 
  group_by(genre) %>% 
  summarise(sum(global_sales)) %>% 
  rename("total_sales" = "sum(global_sales)") %>% 
  arrange(desc(total_sales))
```

```{r}
total_sales_by_genre <- total_sales_by_genre %>% 
  drop_na()
```

```{r}
games_raw 
```

```{r}
breakdown_sales_by_genre <- games_raw %>% 
  group_by(genre) %>% 
  summarise(sum(na_sales), sum(eu_sales), sum(jp_sales), sum(other_sales)) %>% 
  rename("total_na_sales"= "sum(na_sales)", "total_eu_sales" = "sum(eu_sales)", "total_jp_sales" = "sum(jp_sales)", "total_other_sales" = "sum(other_sales)")
```

```{r}
total_sales_by_genre # this seems to have some rounding differences compared to breakdown, so i'll retire this one 
```
how does the sales for the top 3 genres look in each region?


```{r}
breakdown_sales_by_genre <- breakdown_sales_by_genre %>% 
  group_by(genre) %>% 
  mutate(total_sales = sum(total_na_sales + total_eu_sales + total_jp_sales + total_other_sales)) %>% 
  drop_na()
```
```{r}

breakdown_sales_by_genre %>% 
  filter(genre %in% c("Action", "Sports", "Shooter")) %>% 
  ggplot(aes(x = total_sales, y = genre))+
  geom_col() +
  geom_col(aes(x = total_na_sales), fill = "green")+
  geom_col(aes(x = total_eu_sales), fill = "red") +
  geom_col(aes(x = total_jp_sales), fill = "blue") 

# this looks shit
```

What about trends? How did each genres sales adjust every 5 or so years?

```{r}
games_raw %>% 
  filter(year_of_release == "2016")

games_raw %>% 
  mutate(year_of_release = as.integer(year_of_release)) %>% 
  distinct(year_of_release) %>% 
  arrange(year_of_release)

```

```{r}
sales_2019 <- read_csv("raw_data/sales-2019.csv")
```

```{r}
sales_2019 %>% 
  distinct(Year) %>% 
  arrange(desc(Year))
```
```{r}
sales_2019 %>% 
  filter(Year == "2019") %>% 
  select(Name, Year, Platform)

# data for 2020 is total nonsense. Some information in 2019 is incorrect.
```
# Going off the fact that there is the majority of usable information i am able to get is from 2019 or before, we're just going to pretend we're living in an 
# alternative 2019

As such, I am dropping all data from 2020 in this dataset 

```{r}
sales_2019 <- sales_2019 %>% 
  filter(Year != "2020")
```

# Looking at backloggd again

```{r}
backloggd
```
```{r}
# creating a range_rating column to reduce noise when it comes to plotting results
backlogged <- backloggd %>% 
  mutate(rating_range = case_when(
    rating < 5 & rating >= 4 ~ "4+",
    rating < 4 & rating >= 3 ~ "3 to 4",
    rating < 3 & rating >= 2 ~ "2 to 3",
    rating < 2 & rating >= 1 ~ "1 to 2",
    rating < 1 ~ ">1",
    TRUE ~ "No rating"
  ))
```

## DIFFICULTIES WITH THE DATA

After having little success attempting to get a more up to date data set, i've decided to stick with what I already have - Given more time, i would have liked
to have run the steam/steam spy script to scrape all the steam data, but unfortunately i couldn't commit 3 days to it.
There doesn't seem to be much in the way of modern sales data, with most companies not releasing figures unless its to do with a milestone.
Genres are quite vague - While it would be nice to have tags like "Open World", "Rouge-like/lite", we instead mostly have "Action" "Adventure", "Indie", which
are not hugely descriptive. This might make recommending a genre to work on harder

----------------------------------

# DAY 3

```{r}
sales_2019 %>% 
  summary()
```
All of the VGchartz scores are empty, so it can go. Also, same as above, there's no such genre as Platform

```{r}
sales_2019 <- sales_2019 %>% 
  clean_names() %>% 
  select(-vg_chartz_score) %>% 
  mutate(genre = case_when(
    genre == "Platform" ~ "Platformer",
    TRUE ~ genre
  ))
  
```

```{r}
games_raw
```

```{r}
sales_2019 %>% 
  group_by(name) %>% 
  summarise(sum(total_shipped)) %>% 
  arrange(desc(`sum(total_shipped)`)) 

# total shipped might not be the best metric for sales, but better than nothing
```

```{r}
sales_2019 %>% 
  distinct(year) %>% 
  arrange(desc(year))
```
```{r}
sales_2019 <- sales_2019 %>% 
  filter(year != 1970)
```

1970 is nonsense. dropping entire year

```{r}
# adding column to use for showing trends over time
sales_2019 <- sales_2019 %>% 
  mutate(five_year_period = case_when(
    year <= 2019 & year >= 2014 ~ "2014 - 2019",
    year <= 2013 & year >= 2008 ~ "2008 - 2013",
    year <= 2007 & year >= 2002 ~ "2002 - 2007",
    year <= 2001 & year >= 1996 ~ "1996 - 2001",
    year <= 1995 & year >= 1991 ~ "1991 - 1995",
    year <= 1990 & year >= 1985 ~ "1985 - 1990",
    year <= 1984 & year >= 1981 ~ "1981 - 1984",
    year < 1981 ~ "1980 and before",
    TRUE ~ "this shouldnt appear"
  ), .after = year)
```

```{r}
sales_2019 %>% 
  group_by(five_year_period) %>% 
  count(genre) %>% 
  slice_max(n = 2, n) %>% 
  ggplot(aes(x = five_year_period, y = n, fill = genre)) +
  geom_col(colour = "black") +
  labs(
    title = "Most Common Genres Over Time",
    subtitle = "Shown over 5 year intervals",
    caption = "From 2019 games sales data"
  ) +
  scale_fill_manual(values = c(
    "Platformer" = "#04E762",
    "Action" = "#DC0073",
    "Sports" = "#008BF8",
    "Misc" = "#f5b700",
    "Shooter" = "#390099"
  )) +
  theme_light() +
  theme(axis.text.x = element_text(angle = 25, hjust = 0.5, size = 9, face = "bold", vjust = 0.8)) +
  theme(axis.line = element_line(colour = "black"))+
  theme(axis.text.y = element_text(size = 9, face = "bold")) +
  xlab("Interval") +
  ylab("Number of Games in the genre released") +
  theme(axis.title.x = element_text(face = "italic", size = 10)) +
  theme(axis.title.y = element_text(face = "italic", size = 10)) +
  theme(plot.caption = element_text(size = 7, hjust = 1.25)) +
  labs(fill = "Genre")

# Misc isnt very descriptive or helpful - in terms of recommending making something to someone it means essentially "try anything"
```

```{r}

# PLOT SHOWING MOST COMMON GENRE OF GAMES - NOT NECESSARILY BEST SELLING
sales_2019 %>% 
  group_by(five_year_period) %>% 
  filter(genre != "Misc") %>% 
  count(genre) %>% 
  slice_max(n = 2, n) %>% 
  ggplot(aes(x = five_year_period, y = n, fill = genre)) +
  geom_col(colour = "black") +
  labs(
    title = "Most Common Genres Over Time",
    subtitle = "Shown over 5 year intervals - Excluding 'Misc' genre",
    caption = "From 2019 game sales data"
  ) +
   scale_fill_manual(values = c(
   "Platformer" = "#04E762",
    "Action" = "#DC0073",
    "Sports" = "#008BF8",
   # "Misc" = "#f5b700",
    "Shooter" = "#390099",
    "Adventure" = "#8ac926",
    "Role-Playing" = "#ff6b35"
   )) +
  theme_light() +
  theme(axis.text.x = element_text(angle = 25, hjust = 0.5, size = 9, face = "bold", vjust = 0.8)) +
  theme(axis.line = element_line(colour = "black"))+
  theme(axis.text.y = element_text(size = 9, face = "bold")) +
  xlab("Interval") +
  ylab("Number of Games in the genre released") +
  theme(axis.title.x = element_text(face = "italic", size = 10)) +
  theme(axis.title.y = element_text(face = "italic", size = 10)) +
  theme(plot.caption = element_text(size = 7, hjust = 1.25)) +
  labs(fill = "Genre")
         
```

```{r}
sales_2019 %>% 
  filter(five_year_period == "2019 - 2014") %>% 
  filter(genre == "Misc")
```
This is slightly concerning - a lot of these titles could easily have a genre that isn't the cure-all "Misc" - 
Include both graphs - one with misc, one excluding it

```{r}
games_raw %>% 
  filter(genre == "Misc")
```
What about a similar plot for steam games?

```{r}
steam
```
```{r}
steam_years <- steam %>% 
  mutate(release_year = year(release_date),.after = release_date)
```
```{r}
steam_years %>% 
  mutate(length_genre = nchar(genres),.after = name) %>% 
  arrange(desc(length_genre))
```

```{r}
steam_years %>% 
  distinct(release_year) %>% 
  arrange(desc(release_year))
```
```{r}
steam_years <- steam_years %>%  
  separate(col = genres, sep = ";", into = paste0("Genre", seq_len(max(nchar(.$genres))))) %>%  # this is absolutely horrendous, but it gets me all the genres into separate columns so whatever
  select(-Genre14:-Genre180) %>% 
  pivot_longer(cols = Genre1:Genre13, names_to = "genres") %>% 
  drop_na(value) %>% # ok now we can make the year intervals and group them to find what genres were popular 
  mutate(year_range = case_when(
    release_year <= 2019 & release_year >= 2016 ~ "2016 - 2019",
    release_year <= 2015 & release_year >= 2012 ~ "2012 - 2015",
    release_year <= 2011 & release_year >= 2009 ~ "2009 - 2011",
    release_year <= 2008 & release_year >= 2005 ~ "2005 - 2008",
    release_year <= 2004 & release_year>= 2000 ~ "2000 - 2004",
    release_year < 2001 ~ "Before 2000",
    TRUE ~ "this shouldnt appear"
  ),.after = release_year) 
```

```{r}
steam_years %>% 
  filter(year_range == "2000 - 2004")
```
```{r}
steam_years %>% 
  group_by(year_range) %>% 
  count(value) %>% 
  slice_max(n = 2, n) %>% 
  arrange(desc(n))  %>% 
  filter(year_range != "Before 2000") %>% 
  ggplot(aes(x = year_range, y = n, fill = value)) +
  geom_col(colour = "black") +
  labs(
    title = "Most Common Genres Over Time",
    subtitle = "Shown over 3-4 year intervals",
    caption = "From 2019 Steam/Steam Spy data"
  ) +
  scale_fill_manual(values = c(
    "Indie" = "#04E762",
    "Action" = "#DC0073"
  )) +
  theme_light() +
  theme(axis.text.x = element_text(angle = 25, hjust = 0.5, size = 9, face = "bold", vjust = 0.8)) +
  theme(axis.line = element_line(colour = "black"))+
  theme(axis.text.y = element_text(size = 9, face = "bold")) +
  xlab("Interval") +
  ylab("Number of Games in the genre released") +
  theme(axis.title.x = element_text(face = "italic", size = 10)) +
  theme(axis.title.y = element_text(face = "italic", size = 10)) +
  theme(plot.caption = element_text(size = 7, hjust = 1.25)) +
  labs(fill = "Genre")
```

```{r}
# Happy with this one as a comparison point
steam_years %>% 
  filter(release_year >= 2009) %>% 
  group_by(release_year) %>% 
  count(value) %>% 
  slice_max(n = 2, n) %>% 
  arrange(desc(n))  %>% 
  ggplot(aes(x = release_year, y = n, fill = value)) +
  geom_col(colour = "black") +
  labs(
    title = "Most Common Genres Over Time",
    subtitle = "Shown year by year from 2009 until May 2019",
    caption = "From 2019 Steam/Steam Spy data"
  ) +
   scale_fill_manual(values = c(
     "Indie" = "#04E762",
     "Action" = "#DC0073",
     "Casual" = "#008BF8",
     "Adventure" = "#f5b700"
   )) +
  theme_light() +
  theme(axis.text.x = element_text(angle = 25, hjust = 0.5, size = 9, face = "bold", vjust = 0.8)) +
  theme(axis.line = element_line(colour = "black"))+
  theme(axis.text.y = element_text(size = 9, face = "bold")) +
  xlab("Interval") +
  ylab("Number of Games in the genre released") +
  theme(axis.title.x = element_text(face = "italic", size = 10)) +
  theme(axis.title.y = element_text(face = "italic", size = 10)) +
  theme(plot.caption = element_text(size = 7, hjust = 1.25)) +
  scale_x_continuous(breaks = c(2009, 2010, 2011, 2012, 2013, 2014, 2015, 2016, 2017, 2018, 2019)) +
  labs(fill = "Genre")
```


```{r}
steam_years %>% 
  filter(release_year == 2019)
```


```{r}
steam_years %>% 
  mutate(month = month(release_date)) %>% 
  filter(release_year == 2019) %>% 
  select(month) %>% 
  arrange(desc(month))
```
```{r}
backloggd
```

```{r}
backloggd_genres <- backloggd %>% 
  pivot_longer(cols = genre_tag:genre_tag_7, names_to = "list", values_to = "genre") %>% 
  drop_na(genre)
```

```{r}
# ok now i've definitely gotten rid of everything that hasnt released
backloggd_genres <- backloggd_genres %>% 
  mutate(release_year = year(release_date)) %>% 
  filter(-years_since_release < 0.01)
```

```{r}
backloggd_genres %>% 
  distinct(release_year) %>% 
  arrange(desc(release_year))
```
```{r}
backloggd_genres <- backloggd_genres %>%   
  mutate(intervals = case_when(
   release_year <= 2023 & release_year >= 2020 ~ "2020 - 2023",
    release_year <= 2019 & release_year >= 2014 ~ "2014 - 2019",
    release_year <= 2013 & release_year >= 2008 ~ "2008 - 2013",
    release_year  <= 2007 & release_year  >= 2002 ~ "2002 - 2007",
    release_year  <= 2001 & release_year  >= 1996 ~ "1996 - 2001",
    release_year  <= 1995 & release_year  >= 1991 ~ "1991 - 1995",
    release_year  <= 1990 & release_year  >= 1985 ~ "1985 - 1990",
    release_year  <= 1984 & release_year  >= 1981 ~ "1981 - 1984",
    release_year  < 1981 ~ "1980 and before",
    TRUE ~ "this shouldnt appear"
  )) 
```

```{r}
# This isn't showing the most popular genres in a timeframe, more of an insight into what people are playing
# Granted, Backloggd isn't the biggest service in the world, but it's a good idea of what people like, and still play
backloggd_genres %>% 
  mutate(genre = case_when(
    genre == "Platform" ~ "Platformer",
    TRUE ~ genre
  )) %>%
  filter(intervals != "1980 and before") %>% 
  filter(intervals != "1981 - 1984") %>% 
  group_by(intervals) %>% 
  count(genre) %>% 
  slice_max(n = 2, n) %>% 
  ggplot(aes(x = intervals, y = n, fill = genre)) +
  geom_col(colour = "black") +
   labs(
     title = "What do people still play?",
     subtitle = "Split into Genre and Release Year",
     caption = "From March 2023 Backloggd data"
   ) +
   scale_fill_manual(values = c(
   "Platformer" = "#04E762",
   #"Action" = "#DC0073",
   #"Sports" = "#008BF8",
   #"Misc" = "#f5b700",
   "Shooter" = "#390099",
   "Adventure" = "#8ac926",
   "RPG" = "#ff6b35"
   )) +
   theme_light() +
   theme(axis.text.x = element_text(angle = 25, hjust = 0.5, size = 9, face = "bold", vjust = 0.8)) +
   theme(axis.line = element_line(colour = "black"))+
   theme(axis.text.y = element_text(size = 9, face = "bold")) +
   xlab("Release window") +
   ylab("How many people have played ") +
   theme(axis.title.x = element_text(face = "italic", size = 10)) +
   theme(axis.title.y = element_text(face = "italic", size = 10)) +
   theme(plot.caption = element_text(size = 7, hjust = 1.25)) +
   labs(fill = "Genre")
```

# We have established that Indie, Action and Adventure games seem to be the most popular - But what examples of these are there?

